### 2015-11-04 paper.Rmd
starting to show analyses

We can fit a model to the minke whale data, setting the truncation at 1.5km and using the default options in \code{ds} very simply:
```{r minke-hn}
minke_hn <- ds(minke, truncation=1.5)
```
**Figure???** shows the result of calling \code{plot} on the resulting model object.

@@

@@

* qq plots
* hessian/convergence
* monotonicity
* AIC -- what else?

>>>>

### Minke whale

We can fit a model to the minke whale data, setting the truncation at 1.5km and using the default options in \code{ds} very simply:
```{r minke-hn}
minke_hn <- ds(minke, truncation=1.5)
```
**Figure???** shows the result of calling \code{plot} on the resulting model object. We can also call \code{summary} on the model object to get summary information about the fitted model (though we postpone this until the next section).

@@

We can specify the form of the detection function via the \code{model=df(...)} argument to \code{ds}. For example, fitting a hazard rate model with cosine adjustments of order 2 can be specified as:
```{r minke-hr-cos}
minke_hrcos <- ds(minke, truncation=1.5, model=df(model=~hr+cos(2)))
```

By default \code{ds} assumes that the data given to it is line transect, but we can switch to points using \code{transect="points"}. Including covariates in the scale is via the `scale=~...` argument to `df`; a hazard-rate model for the amakihi that includes observer as a covariate (and truncating at 82.5m, given in @Marques:2007ey) can be specified by:
```{r amakihi-hr}
amakihi_hr_obs <- ds(amakihi, truncation=82.5, model=df(model=~hr, scale=~obs), transect="point")
```

@@

```{r minke-hn-summary}
summary(minke_hn)
```

* summary results
* qq plots
* hessian/convergence
* monotonicity
* AIC -- what else?
